Interspecies comparisons of Mg/Ca ratios in limpet shells

### 2024-05-30 Manuscript.qmd
added data

---
title: "Manuscript"
subtitle: A Short Subtitle
author:
  - name: Niklas Hausmann
    affiliations:
      - name: Leibniz Zentrum für Archäologie
        address: Ludwig-Lindenschmit-Forum 1
        city: Mainz
        country: Germany
        postal-code: 55116
    orcid: 0000-0000-0000-0000
    email: niklas@palaeo.eu
    attributes:
        corresponding: true
abstract: |
  This document is a template demonstrating the Aps format.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Palaeo^3^
      formatting: preprint
      model: 3p
      cite-style: authoryear
output:
  units: cm
---

```{r}
#| label: Libray and datasets
#| echo: FALSE
#| message: FALSE
#| warning: FALSE

@@

```{r}
#| label: Raw Data
#| fig-cap: Raw Mg/Ca and δ^18^O Data
#| fig-height: 30
#| fig-width: 8

P1 <- MgCa %>% 
  filter(std<0.1) %>% 
  # filter(mg_ca<0.7) %>% 
  # filter(dist<10) %>% 
ggplot()+
  aes(dist,mg_ca)+
  geom_path(col="firebrick")+
  # xlim(0,10)+
  facet_wrap(~sampleID,ncol=1,scales = "free")

P2 <- D18O %>% 
  filter(sampleID %in% MgCa$sampleID) %>% 
  ggplot()+
  aes(dist,d18O)+
  geom_path(col="cornflowerblue")+
  scale_y_reverse()+
  facet_wrap(~sampleID,scales = "free",ncol=1)

P1|P2

```{r}
#| label: DTW Analysis

@@

```{r}
#| label: Correlation Graphs 
#| fig-cap: Correlation graphs for all specimens
#| fig-height: 20
#| fig-width: 10

@@

>>>>

---
title: "Interspecies comparisons of Mg/Ca ratios in limpet shells"
author:
  - name: Niklas Hausmann
    affiliations:
      - name: Leibniz Zentrum für Archäologie
        address: Ludwig-Lindenschmit-Forum 1
        city: Mainz
        country: Germany
        postal-code: 55116
    orcid: 0000–0002–4381–8334
    email: niklas@palaeo.eu
    attributes:
      corresponding: true
  - name: Donna Surge
    affiliations:
      - name: University of North Carolina
        address: 104 South Road, 225 Geology Building
        city: Chapel Hill, NC
        country: US
        postal-code: 27599-3315
  - name: Francisco Zangrando
    affiliations:
      - name: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas)
        address: Avenida Maipú 305
        city: Ushuaia
        country: Argentina
        postal-code: V9410BJA
  - name: Angelica Tivoli
    affiliations:
      - name: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas)
        address: Avenida Maipú 305
        city: Ushuaia
        country: Argentina
        postal-code: V9410BJA
  - name: Ivan Briz-Godino
    affiliations:
      - name: 
        address: 
        city: 
        country: Spain
        postal-code: 
abstract: |
  This document is a template demonstrating the Aps format.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Palaeo^3^
      formatting: preprint
      model: 3p
      cite-style: authoryear
output:
  units: cm
---

# Introduction {#Introduction}

```{r Libray and datasets}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE

@@

# Methods {#Methods}

```{r DTW Analysis}

@@

# Results {#Results}

```{r Correlation Graphs }
#| fig-cap: Correlation graphs for all specimens
#| fig-height: 20
#| fig-width: 10

@@

| Species            | Locality       | Specimen | Correlation R^2^ | Study                                                          |
|-------------------|---------------|---------------|---------------|---------------|
| *Patella depressa* | Northern Spain | LAN541   | 0.87             | [**10.3390/app11072959**](https://doi.org/10.3390/app11072959) |
|                    |                | LAN545   | 0.86             |                                                                |
|                    |                | LAN554   | 0.78             |                                                                |
|                    |                | LAN559   | 0.82             |                                                                |
| Patella caerulea   | Croatia        | ISTPC1   | 0.9              | 10.1038/s41598-019-39959-9                                     |
|                    |                | ISTPC2   | 0.84             |                                                                |
|                    | Crete          | AF1911A  | 0.91[^1]         |                                                                |
|                    |                | AF3003A  | 0.92[^2]         |                                                                |
|                    | Israel         | AKKPC2   | 0.96             |                                                                |
|                    |                | AKKPC3   | 0.89             |                                                                |
|                    |                | FRMPC1   | 0.84             |                                                                |
|                    |                | FRMPC2   | 0.96             |                                                                |
|                    | Libya          | MO31A    | 0.83             |                                                                |
|                    |                | MP64A    | 0.33             |                                                                |
|                    |                | MP67A    | 0.96             |                                                                |
|                    |                | MP68A    | 0.81             |                                                                |
|                    | Malta          | MA10     | 0.82             |                                                                |
|                    | Tunisia        | TUNPC1   | 0.81             |                                                                |
|                    |                | TUNPC2   | 0.78             |                                                                |
|                    | Turkey         | ANTPC1   | 0.95             |                                                                |
|                    |                | ANTPC2   | 0.93             |                                                                |
|                    |                | KIZPC1   | 0.94             |                                                                |
|                    |                | KIZPC2   | 0.86             |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |
|                    |                |          |                  |                                                                |

: Overview of comparative correlations {#tab:correlations}

[^1]: SST only, no other geochemical data available

[^2]: SST only, no geochemical data available

### 2024-05-30 Manuscript.tex
added data

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  super,
  preprint,
  3p]{elsarticle}

@@

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Palaeo3}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Manuscript},
  pdfauthor={Niklas Hausmann},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Manuscript \\\large{A Short Subtitle} }
\author[1]{Niklas Hausmann%
\corref{cor1}%
}
 \ead{niklas@palaeo.eu}

\affiliation[1]{organization={Leibniz Zentrum für
Archäologie},addressline={Ludwig-Lindenschmit-Forum
1},city={Mainz},country={Germany},countrysep={,},postcode={55116},postcodesep={}}

@@

\begin{verbatim}
 [1] "QG1-7188-1" "QG1-7189-2" "QG2-1061-1" "QG2-1064-1" "QG2-7180-1"
 [6] "QG2-7180-2" "QG1-7246-1" "ND-1016-3"  "ND-1016-4"  "NM-1016-1" 
[11] "NM-1016-3" 
\end{verbatim}

\begin{verbatim}
character(0)
\end{verbatim}

\begin{verbatim}
[1] "ND-1016-1" "NM-1016-5"
\end{verbatim}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  3p]{elsarticle}

@@

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Palaeo3}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Interspecies comparisons of Mg/Ca ratios in limpet shells},
  pdfauthor={Niklas Hausmann; Donna Surge; Francisco Zangrando; Angelica Tivoli; Ivan Briz-Godino},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Interspecies comparisons of Mg/Ca ratios in limpet shells}
\author[1]{Niklas Hausmann%
\corref{cor1}%
}
 \ead{niklas@palaeo.eu} 
\author[2]{Donna Surge%
%
}

\author[3]{Francisco Zangrando%
%
}

\author[3]{Angelica Tivoli%
%
}

\author[4]{Ivan Briz-Godino%
%
}

\affiliation[1]{organization={Leibniz Zentrum für
Archäologie},addressline={Ludwig-Lindenschmit-Forum
1},city={Mainz},country={Germany},countrysep={,},postcode={55116},postcodesep={}}
\affiliation[2]{organization={University of North
Carolina},addressline={104 South Road, 225 Geology
Building},city={Chapel Hill,
NC},country={US},countrysep={,},postcode={27599-3315},postcodesep={}}
\affiliation[3]{organization={CONICET (Consejo Nacional de
Investigaciones Científicas y Técnicas)},addressline={Avenida Maipú
305},city={Ushuaia},country={Argentina},countrysep={,},postcode={V9410BJA},postcodesep={}}
\affiliation[4]{organization={},country={Spain},countrysep={,},postcodesep={}}

@@
